%%%
\acknowledgments

I would like to express my deepest appreciation and gratitude to my guide Prof.
Saravanan Vijayakumaran for his guidance and constant supervision and help throughout the last 18 months. 
His insightful suggestions and comments have time and again helped me get a more in-depth understanding of the field.
His most valuable lesson for me, from amongst many others, was to be persistent especially in times when things are not going as planned. 
Not only did he offer consistent assistance with regards to the academic work but also gave invaluable suggestions in helping me carve out my career path. 
I also thank the Bharti Centre for Communication at IIT Bombay and Vibha ma'am particularly for providing necessary logistical support.
Thanks are also due to Arijit Dutta of IIT, Bombay for his many useful remarks and discussions about the project and otherwise. 
I also acknowledge the help offered by my brother Piyush Bagad (Wadhwani AI) in understanding Python as well as in running simulations. 
I would also like to thank my dear friend Madhura Pawar for her constant encouragement
which helped me work towards my goal even when things weren't working out.
Finally, I express gratitude towards my family for giving me the opportunities and freedom in choosing research as my career.





\signature{24 June 2020}
%\signature[Indian Institute of Technology Bombay]{\today}

%========================================================================

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../mainrep"
%%% End: 